Cheat Sheet for PFPL

### 2016-03-15 pfpl/cheatsheet.tex
Back to desktop
Fix title and quantifiers

37& 64 & $\mathcal{|[}\it{x/e/f}\mathcal{]|}\it{e'}$ & Script bracket & Function substitution & Function substitution \\

@@

51& 133 & $ \cong $ & Tilde equal & Isomorphism & Isomorphism \\
\end{tabular}
\subsection*{VII. Variable Types}
\subsubsection*{17 Abstract Types}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
52 & 149 & $\exists(t.\tau)$ & Exists & Interface & Defines an interface \\
53 & 153 & $\forall(t.\tau\longrightarrow\tau_2)$ & Forall & Universal type & Defines universal type \\
\end{tabular}

>>>>

37& 64 &  $|[x/e/f]|e'$ & Script bracket & Function substitution & Function substitution \\

@@

51& 133 & $ \cong $ & Tilde equal & Isomorphism & Isomorphism \\
\end{tabular}
\subsection*{VII. Variable Types}
\subsubsection*{17 Abstract Types}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\
52 & 149 & $\exists(t.\tau)$ & Existential quantifier & Exists & Defines an interface \\
53 & 153 & $\forall(t.\tau\longrightarrow\tau_2)$ & Universal quantifier & For all & Defines universal type \\
\end{tabular}
